Fractional Types

### 2019-11-22 fracGC/p.tex
start on Related Work. Remove duplicates in bib file to placate bibtex.

Quantum wire recycling~\cite{PhysRevA.94.042337}

Quantum runtime assertion~\cite{DBLP:journals/cal/ZhouB19}

QWIRE~\cite{Paykin:2017:QCL:3009837.3009894}

Yokoyama, T., Axelsen, H.B., Glück, R.: Principles of a reversible
programming language. In: Conference on Computing Frontiers, CF,
pp. 43–54. ACM Press (2008)

Trace as a lens? This basically says, in the language of Lens, that
when $A$ is isomorphic to $X \times Y$ and $B$ is isomorphic to
$Z \times Y$, then $X$ is isomorphic to $Y$. Another way to think of
it: for all isomorphic $A$ and $B$, whenever they can be factored with
a common complement ($Y$), then the ``other pieces'' (here $X$ and
$Y$) are automatically isomorphic.

Positive rational numbers are a model. Apparently there is a
categorification
\url{https://alistairsavage.ca/pubs/Copelli-Categorification_of_the_Nonnegative_Rational_Numbers.pdf}

>>>>

There has been ample work on ancillae before us.  For example%
\cite{PhysRevA.94.042337} explicitly represent the lifetime of
quantum wires, enable quantum wires to be recycled, leading
to more efficient circuits.  Interesting applications of
ancillae is in the recent paper~\cite{DBLP:journals/cal/ZhouB19}
on Quantum runtime assertions.  In section~\ref{sub:id}, we
already mentionned dynamic assertion of entanglement; they
also show how to provide (dynamic) assertions on classical
states, and testing of superposition states.  Our techniques
should combine with theirs to provide even more possibilities
for dynamic asserctions. Ancilla management is a complex
business, and the verified circuit compiler
ReVerC~\cite{amy2017verified} goes to great pains to
ensure that ancilla are dealt with properly.  Both
QCL~\cite{omer2002procedural} and Quipper~\cite{Green:2013:QSQ:2491956.2462177}
also do automatic (but not certified) ancilla management during code
generation.  This remains an active area of research, as
outlined in the CACM paper~\cite{valiron2015programming}.

Another interesting avenue is to understand how to merge 
pointed $\Pi$ with another simple language for quantum
computing: QWIRE~\cite{Paykin:2017:QCL:3009837.3009894}.
QWIRE has many desirable meta-properties that have been
formally proven to hold.  Our respective paradigms appear eminently compatible,
however their language has an unguarded \texttt{discard} directive that
may lead to erroneous circuits. For example, their circuit
reversing operation is partial, whereas ours is provably total.

When looking at higher-level reversible languages, Janus
comes to mind~\cite{lutz1982janus}.  More recently, \cite{Yokoyama:2008:PRP}
shows how to do clean, i.e. \emph{garbage free} computation. It
would certainly be intriguing to augment Janus with a certified
garbage collection discipline such as ours, so that one might hope
that the resulting computations might be more efficiently done.

%Trace as a lens? This basically says, in the language of Lens, that
%when $A$ is isomorphic to $X \times Y$ and $B$ is isomorphic to
%$Z \times Y$, then $X$ is isomorphic to $Y$. Another way to think of
%it: for all isomorphic $A$ and $B$, whenever they can be factored with
%a common complement ($Y$), then the ``other pieces'' (here $X$ and
%$Y$) are automatically isomorphic.

%Positive rational numbers are a model. Apparently there is a
%categorification
%\url{https://alistairsavage.ca/pubs/Copelli-Categorification_of_the_Nonnegative_Rational_Numbers.pdf}
